Parallel Monte Carlo Synthetic Acceleration Methods for Discrete Transport Problems

### 2013-09-04 doc/dissertation/presentation/defense.tex
reducing msod explanation to one slide

  \begin{itemize}
    {\small
    \item Drekar is a production CFD code using Newton methods with
      FAD
      \medskip
    \item MCLS incorporated into Drekar nonlinear scheme to implement
      FANM
      \medskip
    \item Newton-Krylov method with Aztec GMRES used for benchmark
      comparisons
    \item All methods and problems preconditioned with explicit scheme
      using algebraic multigrid (ML) and leveraged some kind of
      globalization (e.g. backtracking) }
  \end{itemize}

@@

      \small{
        \begin{itemize}
        \item Weaker preconditioning at Ra=\sn{1}{5} case
          \medskip
        \item $\eta_k = \gamma \Big(
          \frac{||\ve{F}(\ve{u}_k)||}{||\ve{F}(\ve{u}_{k-1})||}
          \Big)^{\alpha}$
          \medskip
        \item Constant forcing term for Ra=\sn{1}{6} case
          \medskip
        \item RDA applied in all cases
        \end{itemize}
      }

@@

      \small{
        \begin{itemize}
        \item Forcing term selection can significantly modify nonlinear
          convergence
        \item Newton-Krylov always had larger forcing terms
        \item At Re=700, MCSA histories doubled and RDA fill increased
          from 200 to 300
        \end{itemize}
      }

@@

%%---------------------------------------------------------------------------%%
\begin{frame}{Multiple-Set Overlapping-Domain Decomposition}

    \begin{column}{0.5\textwidth}
      \begin{figure}[htpb!]
        \begin{center}
          \scalebox{0.75}{ \input{msod_example.pdftex_t} }
        \end{center}
        \caption{\small Overlapping domain example illustrating how
          domain overlap can reduce communication costs.}
      \end{figure}
    \end{column}

    \begin{column}{0.5\textwidth}
      \begin{itemize}
      \item Developed by Wagner and colleagues in 2010
        \medskip
      \item Each set contains the full domain
        \medskip
      \item Multiple sets replicate the domain
        \medskip
      \item Domains overlap within a set
        \medskip
      \item Redundancy for resiliency (and useful work)
      \end{itemize}
    \end{column}

  \let\thefootnote\relax\footnote{\tiny{Wagner et. al., "Hybrid and
      parallel domain-decomposition methods development to enable
      Monte Carlo for reactor analysis", Joint International
      Conference on Supercomputing in Nuclear Applications and Monte
      Carlo (SNA+MC 2010), 2010.}}
\end{frame}

@@

      \begin{figure}[htpb!]
        \begin{center}
          \scalebox{0.2}{ \input{msod_construction.pdftex_t} }
        \end{center}
        \caption{\small MSOD construction.}
      \end{figure}

@@

      \begin{figure}[htpb!]
        \begin{center}
          \scalebox{0.2}{ \input{msod_tally.pdftex_t} }
        \end{center}
        \caption{\small MSOD tally reduction.}
      \end{figure}

@@

    \begin{algorithm}[H]
      \begin{algorithmic}[1]
        \tiny
        \STATE build MSOD domain
        \STATE build Monte Carlo source
        \STATE build Monte Carlo tally
        \STATE perform parallel Neumann-Ulam transport in each set
        \STATE combine set tallies
        \STATE combine block tallies
      \end{algorithmic}
      \caption{MSOD Transport Sequence}
    \end{algorithm}

>>>>

  \begin{itemize}
    {\small
    \item Drekar is a production CFD code using Newton methods with
      FAD
      \medskip
    \item MCLS incorporated into Drekar nonlinear scheme to implement
      FANM
      \medskip
    \item Newton-Krylov method with Aztec GMRES used for benchmark
      comparisons
    \item All methods and problems preconditioned with explicit scheme
      using algebraic multigrid (ML) and leveraged some kind of
      globalization (e.g. backtracking) with RDA
    }
  \end{itemize}

@@

      \small{
        \begin{itemize}
        \item Weaker preconditioning at Ra=\sn{1}{5} case
          \medskip
        \item Constant forcing term for Ra=\sn{1}{6} case
        \end{itemize}
      }

@@

      \small{
        \begin{itemize}
        \item $\eta_k = \gamma \Big(
          \frac{||\ve{F}(\ve{u}_k)||}{||\ve{F}(\ve{u}_{k-1})||}
          \Big)^{\alpha}$
        \item Newton-Krylov always had larger forcing terms
        \item At Re=700, MCSA histories doubled and RDA fill increased
          from 200 to 300
        \end{itemize}
      }

@@

@@

    \begin{column}{0.52\textwidth}

      \begin{figure}[t!]
        \begin{center}
          \scalebox{0.275}{ \input{msod_construction.pdftex_t} }
        \end{center}
        \caption{\small MSOD construction.}
      \end{figure}

@@

    \begin{column}{0.48\textwidth}

      \begin{figure}[t!]
        \begin{center}
          \scalebox{0.2}{ \input{msod_tally.pdftex_t} }
        \end{center}
        \caption{\small MSOD tally reduction.}
      \end{figure}

      \begin{itemize}
        {\small
        \item Multiple sets replicate the domain
        \item Domains overlap within a set
        \item Each set contains the full domain
        }
      \end{itemize}

@@

  \let\thefootnote\relax\footnote{\tiny{Wagner et. al., "Hybrid and
      parallel domain-decomposition methods development to enable
      Monte Carlo for reactor analysis", Joint International
      Conference on Supercomputing in Nuclear Applications and Monte
      Carlo (SNA+MC 2010), 2010.}}
